---
title: "Ch02 Some Basics"
author: "Stephen CUI"
date: "2023-06-25"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
print(pi)
print(sqrt(2))
```

The beauty of print is that it knows how to format any R value for printing, including structured values such as matrices and lists:
```{r}
print(matrix(c(1, 2, 3, 4), 2, 2))
print(list('a', 'b', 'c'))
```
The print function has a significant limitation, however: it prints only one object at a time. Trying to print multiple items gives this mind-numbing error message
```{r}
print("The zero occurs at", 2 * pi, "radians.")
```

The cat function is an alternative to print that lets you concatenate multiple items into a continuous output:
```{r}
cat("The zero occurs at", 2 * pi, "radians.", "\n")
fib <- c(0, 1, 1, 2, 3, 5, 8, 13, 21, 34)
cat("The first few Fibonacci numbers are:", fib, "...\n")
```
A serious limitation, however, is that it cannot print compound data structures such as matrices and lists.
```{r}
cat(list('a', 'b', 'c'))
```

